Reviewer comments from PeerJ

### 2015-03-24 PeerJ_trackchanges.tex
Edits
LV edits to text and supplement regarding NJ tree

\textbf{Sequence analysis---}For population genetic analyses of sequenced Region 1 and sequenced Region 2 we used the Analysis package from the  Libsequence library \citep{Thornton2003} to calculate pairwise F\textsubscript{ST} between populations and to calculate standard diversity statistics (number of haplotypes, haplotype diversity, Watterson's estimator $\hat\theta_W$, pairwise nucleotide diversity $\hat\theta_\pi$, and Tajima's D). To produce a visual representation of differentiation between sequences and examine patterns in sequence clustering by \emph{Hopscotch} genotype we used Phylip (\url{http://evolution.genetics.washington.edu/phylip.html}) to create neighbor-joining trees with bootstrap-supported nodes (100 repetitions). For creation of trees we also included homologous sequence data from Maize HapMapV2 \citep{Chia2012} for teosinte inbred lines (TILs), some of which are known to be homozygous for the \emph{Hopscotch} insertion (TIL03, TIL17, TIL09), as well as 59 lines of domesticated maize.

>>>>

\textbf{Sequence analysis---}For population genetic analyses of sequenced Region 1 and sequenced Region 2 we used the Analysis package from the  Libsequence library \citep{Thornton2003} to calculate pairwise F\textsubscript{ST} between populations and to calculate standard diversity statistics (number of haplotypes, haplotype diversity, Watterson's estimator $\hat\theta_W$, pairwise nucleotide diversity $\hat\theta_\pi$, and Tajima's D). To produce a visual representation of differentiation between sequences and examine patterns in sequence clustering by \emph{Hopscotch} genotype we used Phylip (\url{http://evolution.genetics.washington.edu/phylip.html}) to create neighbor-joining trees with bootstrap-supported nodes (10,000 repetitions). For creation of trees we also included homologous sequence data from Maize HapMapV2 \citep{Chia2012} for teosinte inbred lines (TILs), some of which are known to be homozygous for the \emph{Hopscotch} insertion (TIL03, TIL17, TIL09), as well as 59 lines of domesticated maize.

### 2015-03-24 Supplement_mbh.tex
edits
LV final edits to table s2
Edits
LV edits to text and supplement regarding NJ tree

\begin{longtable}{>{\stepcounter{rowno}}ccc}

@@

\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} \\

@@

    RIMMA0066 & 2     & 1 \\
    RIMMA0075 & 2     & 1 \\
    RIMMA0077 & 2     & 1 \\
    RIMMA0079 & 2     & 1 \\
    RIMMA0081 & 2     & 1 \\
    RIMMA0084 & 2     & 1 \\
    RIMMA0086 & 2     & 1 \\
    RIMMA0088 & 2     & 1 \\
    RIMMA0089 & 2     & 1 \\
    RIMMA0090 & 2     & 1 \\
    RIMMA0092 & 4     & 1 \\
    RIMMA0094 & 4     & 1 \\
    RIMMA0097 & 2     & 1 \\
    RIMMA0099 & 2     & 1 \\
    RIMMA0100 & 2     & 1 \\
    RIMMA0101 & 2     & 1 \\
    RIMMA0104 & 2     & 1 \\
    RIMMA0108 & 2     & 1 \\
    RIMMA0111 & 6     & 1 \\
    RIMMA0115 & 2     & 1 \\
    RIMMA0117 & 2     & 1 \\
    RIMMA0130 & 2     & 1 \\
    RIMMA0133 & 2     & 1 \\
    RIMMA0134 & 2     & 1 \\
    RIMMA0135 & 2     & 1 \\
    RIMMA0142 & 2     & 0.5 \\
    RIMMA0143 & 4     & 1 \\
    RIMMA0146 & 4     & 1 \\
    RIMMA0149 & 2     & 1 \\
    RIMMA0152 & 2     & 1 \\
    RIMMA0153 & 2     & 1 \\
    RIMMA0154 & 2     & 1 \\
    RIMMA0155 & 2     & 1 \\
    RIMMA0156 & 2     & 1 \\
    RIMMA0157 & 2     & 1 \\
    RIMMA0158 & 2     & 1 \\
    RIMMA0159 & 2     & 1 \\
    RIMMA0160 & 2     & 1 \\
    RIMMA0162 & 2     & 1 \\
    RIMMA0166 & 2     & 1 \\
    RIMMA0167 & 2     & 1 \\
    RIMMA0168 & 2     & 1 \\
    RIMMA0169 & 2     & 1 \\
    RIMMA0172 & 2     & 1 \\
    RIMMA0174 & 4     & 1 \\
    RIMMA0177 & 2     & 1 \\
    RIMMA0178 & 2     & 1 \\
    RIMMA0179 & 2     & 1 \\
    RIMMA0181 & 2     & 1 \\
    RIMMA0183 & 2     & 1 \\
    RIMMA0184 & 2     & 1 \\
    RIMMA0186 & 2     & 1 \\
    RIMMA0187 & 1     & 1 \\
    RIMMA0188 & 2     & 1 \\
    RIMMA0195 & 2     & 1 \\
    RIMMA0196 & 2     & 1 \\
    RIMMA0197 & 2     & 1 \\
    RIMMA0198 & 2     & 1 \\
    RIMMA0199 & 2     & 1 \\
    RIMMA0200 & 2     & 1 \\
    RIMMA0202 & 2     & 1 \\
    RIMMA0203 & 2     & 1 \\
    RIMMA0206 & 2     & 1 \\
    RIMMA0208 & 2     & 1 \\
    RIMMA0209 & 2     & 1 \\
    RIMMA0210 & 2     & 1 \\
    RIMMA0212 & 2     & 1 \\
    RIMMA0213 & 2     & 1 \\
    RIMMA0214 & 2     & 1 \\
    RIMMA0217 & 2     & 1 \\
    RIMMA0218 & 2     & 1 \\
    RIMMA0220 & 2     & 1 \\
    RIMMA0221 & 2     & 1 \\
    RIMMA0222 & 2     & 1 \\
    RIMMA0223 & 2     & 1 \\
    RIMMA0226 & 2     & 1 \\
    RIMMA0227 & 2     & 1 \\
    RIMMA0228 & 2     & 1 \\
    RIMMA0229 & 2     & 1 \\
    RIMMA0230 & 2     & 1 \\
    RIMMA0232 & 2     & 1 \\
    RIMMA0233 & 2     & 1 \\
    RIMMA0235 & 2     & 0.5 \\
    RIMMA0242 & 2     & 1 \\
    RIMMA0243 & 2     & 1 \\
    RIMMA0247 & 4     & 1 \\
    RIMMA0248 & 2     & 1 \\
    RIMMA0249 & 2     & 1 \\
    RIMMA0252 & 2     & 1 \\
    RIMMA0253 & 2     & 1 \\
    RIMMA0254 & 2     & 1 \\
    RIMMA0256 & 2     & 1 \\
    RIMMA0257 & 2     & 1 \\
    RIMMA0258 & 2     & 1 \\
    RIMMA0259 & 2     & 1 \\
    RIMMA0260 & 2     & 1 \\
    RIMMA0262 & 2     & 1 \\
    RIMMA0263 & 2     & 1 \\
    RIMMA0264 & 2     & 1 \\
    RIMMA0265 & 2     & 1 \\
    RIMMA0268 & 2     & 1 \\
    RIMMA0269 & 2     & 1 \\
    RIMMA0270 & 2     & 1 \\
    RIMMA0272 & 2     & 1 \\
    RIMMA0275 & 2     & 1 \\
    RIMMA0276 & 2     & 1 \\
    RIMMA0277 & 2     & 1 \\
    RIMMA0279 & 2     & 1 \\
    RIMMA0280 & 2     & 1 \\
    RIMMA0283 & 2     & 1 \\
    RIMMA0285 & 2     & 1 \\
    RIMMA0288 & 2     & 1 \\
    RIMMA0290 & 2     & 1 \\
    RIMMA0291 & 2     & 1 \\
    RIMMA0292 & 2     & 1 \\
    RIMMA0293 & 2     & 1 \\
    RIMMA0298 & 2     & 1 \\
    RIMMA0302 & 2     & 1 \\
    RIMMA0305 & 2     & 1 \\
    RIMMA0310 & 2     & 1 \\
    RIMMA0312 & 2     & 1 \\
    RIMMA0320 & 2     & 1 \\
    RIMMA0322 & 2     & 1 \\
    RIMMA0324 & 2     & 1 \\
    RIMMA0334 & 2     & 1 \\
    RIMMA0336 & 2     & 1 \\
    RIMMA0337 & 2     & 1 \\
    RIMMA0338 & 2     & 1 \\
    RIMMA0339 & 2     & 1 \\
    RIMMA0340 & 2     & 1 \\
    RIMMA0341 & 2     & 1 \\
    RIMMA0342 & 2     & 1 \\
    RIMMA0344 & 2     & 1 \\
    RIMMA0346 & 2     & 1 \\
    RIMMA0347 & 2     & 1 \\
    RIMMA0350 & 2     & 1 \\
    RIMMA0351 & 2     & 1 \\
    RIMMA0352 & 2     & 1 \\
    RIMMA0357 & 2     & 1 \\
    RIMMA0360 & 18    & 1 \\
    RIMMA0362 & 8     & 1 \\
    RIMMA0363 & 16    & 1 \\
    RIMMA0370 & 17    & 1 \\
    RIMMA0372 & 24    & 1 \\
    RIMMA0373 & 22    & 1 \\
    RIMMA0408 & 2     & 1 \\
    RIMMA0411 & 1     & 1 \\
    RIMMA0413 & 1     & 1 \\
    RIMMA0414 & 1     & 1 \\
    RIMMA0424 & 8     & 0.9 \\
    RIMMA0432 & 1     & 1 \\
    RIMMA0434 & 2     & 0.5 \\
    RIMMA0435 & 1     & 1 \\
    RIMMA0442 & 2     & 1 \\
    RIMMA0443 & 2     & 1 \\
    RIMMA0444 & 2     & 1 \\
    RIMMA0445 & 2     & 1 \\
    RIMMA0446 & 2     & 1 \\
    RIMMA0447 & 2     & 1 \\
    RIMMA0448 & 2     & 1 \\
    RIMMA0449 & 2     & 1 \\
    RIMMA0450 & 2     & 1 \\
    RIMMA0451 & 2     & 1 \\
    RIMMA0452 & 2     & 1 \\
    RIMMA0453 & 2     & 1 \\
    RIMMA0454 & 2     & 1 \\
    RIMMA0455 & 2     & 1 \\
    RIMMA0456 & 2     & 1 \\
    RIMMA0457 & 2     & 1 \\
    RIMMA0458 & 2     & 1 \\
    RIMMA0459 & 2     & 1 \\
    RIMMA0483 & 2     & 1 \\
    RIMMA0490 & 2     & 1 \\
    RIMMA0515 & 2     & 1 \\
    RIMMA0537 & 2     & 1 \\
    RIMMA0550 & 2     & 1 \\
    RIMMA0553 & 2     & 1 \\
    RIMMA0559 & 2     & 1 \\
    RIMMA0561 & 2     & 1 \\
    RIMMA0562 & 2     & 1 \\
    RIMMA0571 & 2     & 1 \\
    RIMMA0572 & 2     & 1 \\
    RIMMA0577 & 2     & 1 \\
    RIMMA0579 & 2     & 1 \\
    RIMMA0590 & 2     & 1 \\
    RIMMA0591 & 2     & 1 \\
    RIMMA0592 & 2     & 1 \\
    RIMMA0593 & 2     & 1 \\
    RIMMA0594 & 2     & 1 \\
    RIMMA0595 & 2     & 1 \\
    RIMMA0596 & 2     & 1 \\
    RIMMA0597 & 2     & 1 \\
    RIMMA0598 & 2     & 1 \\
    RIMMA0599 & 2     & 1 \\
    RIMMA0600 & 2     & 1 \\
    RIMMA0601 & 2     & 1 \\
    RIMMA0602 & 2     & 1 \\
    RIMMA0603 & 2     & 1 \\
    RIMMA0604 & 2     & 1 \\
    RIMMA0605 & 2     & 1 \\
    RIMMA0606 & 2     & 1 \\
    RIMMA0607 & 2     & 1 \\
    RIMMA0608 & 2     & 1 \\
    RIMMA0609 & 2     & 1 \\
    RIMMA0610 & 2     & 1 \\
    RIMMA0611 & 2     & 1 \\
    RIMMA0612 & 2     & 1 \\
    RIMMA0613 & 2     & 1 \\
    RIMMA0622 & 2     & 0.5 \\
    RIMMA0624 & 1     & 1 \\
    RIMMA0629 & 2     & 0.5 \\
    RIMMA0631 & 2     & 0.5 \\
    RIMMA0659 & 2     & 1 \\
    RIMMA0660 & 2     & 1 \\
    RIMMA0678 & 1     & 1 \\
    RIMMA0681 & 2     & 1 \\
    RIMMA0683 & 2     & 1 \\
    RIMMA0684 & 2     & 1 \\
    RIMMA0685 & 4     & 1 \\
    RIMMA0693 & 2     & 1 \\
    RIMMA0694 & 2     & 1 \\
    RIMMA0695 & 1     & 1 \\
    RIMMA0699 & 2     & 1 \\
    RIMMA0704 & 2     & 1 \\
    RIMMA0706 & 2     & 1 \\
    RIMMA0711 & 1     & 1 \\
    RIMMA0713 & 2     & 1 \\
    RIMMA0715 & 2     & 1 \\
    RIMMA0717 & 2     & 1 \\
    RIMMA0718 & 2     & 1 \\
    RIMMA0723 & 2     & 1 \\
    RIMMA0724 & 2     & 1 \\
    RIMMA0725 & 1     & 1 \\
    RIMMA0728 & 1     & 1 \\
    RIMMA0732 & 2     & 1 \\
    RIMMA0734 & 2     & 1 \\
    RIMMA0738 & 2     & 1 \\
    RIMMA0739 & 2     & 1 \\
    RIMMA0744 & 2     & 1 \\
    RIMMA0747 & 1     & 1 \\
    RIMMA0748 & 2     & 1 \\
    RIMMA0749 & 2     & 1 \\
    RIMMA0750 & 2     & 0.5 \\
    RIMMA0751 & 1     & 1 \\
    RIMMA0752 & 1     & 1 \\
    RIMMA0753 & 2     & 1 \\
    RIMMA0755 & 2     & 1 \\

@@

% Appendix S5. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.png}
    \flushleft{Figure S2: Neighbor-joining tree of the sequenced region in the 5' UTR (right; Region 1) and the 66,169 bp upstream region (left; Region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion. EjuA refers to individuals from population Ejutla A, EjuB from Ejutla B, SLO from San Lorenzo, and MSA from La Mesa. Remaining individuals are lines of maize (\emph{Zea mays} ssp. \emph{mays}).}

>>>>

\begin{longtable}{>{\stepcounter{rowno}}cccc}

@@

\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{USDA ID}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} \\

@@

    RIMMA0066 & 27096 & 2     & 1 \\
    RIMMA0075 & 19309 & 2     & 1 \\
    RIMMA0077 & 19313 & 2     & 1 \\
    RIMMA0079 & 19321 & 2     & 1 \\
    RIMMA0081 & 20190 & 2     & 1 \\
    RIMMA0084 & 22439 & 2     & 1 \\
    RIMMA0086 & 22748 & 2     & 1 \\
    RIMMA0088 & 22756 & 2     & 1 \\
    RIMMA0089 & 23392 & 2     & 1 \\
    RIMMA0090 & 23423 & 2     & 1 \\
    RIMMA0092 & 23427 & 4     & 1 \\
    RIMMA0094 & 23447 & 4     & 1 \\
    RIMMA0097 & 23488 & 2     & 1 \\
    RIMMA0099 & 23509 & 2     & 1 \\
    RIMMA0100 & 23518 & 2     & 1 \\
    RIMMA0101 & 23519 & 2     & 1 \\
    RIMMA0104 & 24590 & 2     & 1 \\
    RIMMA0108 & 26022 & 2     & 1 \\
    RIMMA0111 & 26770 & 6     & 1 \\
    RIMMA0115 & 26798 & 2     & 1 \\
    RIMMA0117 & 27045 & 2     & 1 \\
    RIMMA0130 & 28336 & 2     & 1 \\
    RIMMA0133 & 8581 & 2     & 1 \\
    RIMMA0134 & 22632 & 2     & 1 \\
    RIMMA0135 & 22634 & 2     & 1 \\
    RIMMA0142 & 30060 & 2     & 0.5 \\
    RIMMA0143 & 30065 & 4     & 1 \\
    RIMMA0146 & 30863 & 4     & 1 \\
    RIMMA0149 & 30869 & 2     & 1 \\
    RIMMA0152 & 32722 & 2     & 1 \\
    RIMMA0153 & 32728 & 2     & 1 \\
    RIMMA0154 & 32732 & 2     & 1 \\
    RIMMA0155 & 42809 & 2     & 1 \\
    RIMMA0156 & 42872 & 2     & 1 \\
    RIMMA0157 & 42874 & 2     & 1 \\
    RIMMA0158 & 42875 & 2     & 1 \\
    RIMMA0159 & 42878 & 2     & 1 \\
    RIMMA0160 & 65864 & 2     & 1 \\
    RIMMA0162 & 65866 & 2     & 1 \\
    RIMMA0166 & 213696 & 2     & 1 \\
    RIMMA0167 & 213697 & 2     & 1 \\
    RIMMA0168 & 213698 & 2     & 1 \\
    RIMMA0169 & 213699 & 2     & 1 \\
    RIMMA0172 & 213705 & 2     & 1 \\
    RIMMA0174 & 213708 & 4     & 1 \\
    RIMMA0177 & 213715 & 2     & 1 \\
    RIMMA0178 & 213716 & 2     & 1 \\
    RIMMA0179 & 213717 & 2     & 1 \\
    RIMMA0181 & 213719 & 2     & 1 \\
    RIMMA0183 & 213721 & 2     & 1 \\
    RIMMA0184 & 213722 & 2     & 1 \\
    RIMMA0186 & 213724 & 2     & 1 \\
    RIMMA0187 & 213725 & 1     & 1 \\
    RIMMA0188 & 213727 & 2     & 1 \\
    RIMMA0195 & 213781 & 2     & 1 \\
    RIMMA0196 & 213793 & 2     & 1 \\
    RIMMA0197 & 214197 & 2     & 1 \\
    RIMMA0198 & 214293 & 2     & 1 \\
    RIMMA0199 & 214294 & 2     & 1 \\
    RIMMA0200 & 214295 & 2     & 1 \\
    RIMMA0202 & 217407 & 2     & 1 \\
    RIMMA0203 & 217408 & 2     & 1 \\
    RIMMA0206 & 217473 & 2     & 1 \\
    RIMMA0208 & 218005 & 2     & 1 \\
    RIMMA0209 & 218195 & 2     & 1 \\
    RIMMA0210 & 219871 & 2     & 1 \\
    RIMMA0212 & 219882 & 2     & 1 \\
    RIMMA0213 & 219883 & 2     & 1 \\
    RIMMA0214 & 219884 & 2     & 1 \\
    RIMMA0217 & 221872 & 2     & 1 \\
    RIMMA0218 & 221873 & 2     & 1 \\
    RIMMA0220 & 221876 & 2     & 1 \\
    RIMMA0221 & 221877 & 2     & 1 \\
    RIMMA0222 & 221878 & 2     & 1 \\
    RIMMA0223 & 221880 & 2     & 1 \\
    RIMMA0226 & 221889 & 2     & 1 \\
    RIMMA0227 & 222314 & 2     & 1 \\
    RIMMA0228 & 222315 & 2     & 1 \\
    RIMMA0229 & 222316 & 2     & 1 \\
    RIMMA0230 & 222317 & 2     & 1 \\
    RIMMA0232 & 222469 &  2     & 1 \\
    RIMMA0233 & 222470 & 2     & 1 \\
    RIMMA0235 & 222474 & 2     & 0.5 \\
    RIMMA0242 & 222614 & 2     & 1 \\
    RIMMA0243 & 222615 & 2     & 1 \\
    RIMMA0247 & 222639 & 4     & 1 \\
    RIMMA0248 & 222640 & 2     & 1 \\
    RIMMA0249 & 222641 & 2     & 1 \\
    RIMMA0252 & 233002 & 2     & 1 \\
    RIMMA0253 & 233006 & 2     & 1 \\
    RIMMA0254 & 233008 & 2     & 1 \\
    RIMMA0256 & 237000 & 2     & 1 \\
    RIMMA0257 & 257506 & 2     & 1 \\
    RIMMA0258 & 267179 & 2     & 1 \\
    RIMMA0259 & 269743 & 2     & 1 \\
    RIMMA0260 & 269744 & 2     & 1 \\
    RIMMA0262 & 270297 & 2     & 1 \\
    RIMMA0263 & 278713 & 2     & 1 \\
    RIMMA0264 & 278716 & 2     & 1 \\
    RIMMA0265 & 278717 & 2     & 1 \\
    RIMMA0268 & 278721 & 2     & 1 \\
    RIMMA0269 & 278724 & 2     & 1 \\
    RIMMA0270 & 280061 & 2     & 1 \\
    RIMMA0272 & 280853 & 2     & 1 \\
    RIMMA0275 & 311232 & 2     & 1 \\
    RIMMA0276 & 311235 & 2     & 1 \\
    RIMMA0277 & 311236 & 2     & 1 \\
    RIMMA0279 & 311241 & 2     & 1 \\
    RIMMA0280 & 311243 & 2     & 1 \\
    RIMMA0283 & 401757 & 2     & 1 \\
    RIMMA0285 & 414176 & 2     & 1 \\
    RIMMA0288 & 452032 & 2     & 1 \\
    RIMMA0290 & 452045 & 2     & 1 \\
    RIMMA0291 & 452046 & 2     & 1 \\
    RIMMA0292 & 452047 & 2     & 1 \\
    RIMMA0293 & 452048 & 2     & 1 \\
    RIMMA0298 & 483273 & 2     & 1 \\
    RIMMA0302 & 540784 & 2     & 1 \\
    RIMMA0305 & 548792 & 2     & 1 \\
    RIMMA0310 & 550462 & 2     & 1 \\
    RIMMA0312 & 550466 & 2     & 1 \\
    RIMMA0320 & 583896 & 2     & 1 \\
    RIMMA0322 & 583898 & 2     & 1 \\
    RIMMA0324 & 587125 & 2     & 1 \\
    RIMMA0334 & 587153 & 2     & 1 \\
    RIMMA0336 & 607519 & 2     & 1 \\
    RIMMA0337 & 607522 & 2     & 1 \\
    RIMMA0338 & 607593 & 2     & 1 \\
    RIMMA0339 & 607599 & 2     & 1 \\
    RIMMA0340 & 607602 & 2     & 1 \\
    RIMMA0341 & 608465 & 2     & 1 \\
    RIMMA0342 & 608502 & 2     & 1 \\
    RIMMA0344 & 608539 & 2     & 1 \\
    RIMMA0346 & 608618 & 2     & 1 \\
    RIMMA0347 & 608619 & 2     & 1 \\
    RIMMA0350 & 608646 & 2     & 1 \\
    RIMMA0351 & 608652 & 2     & 1 \\
    RIMMA0352 & 608764 & 2     & 1 \\
    RIMMA0357 & 608777 & 2     & 1 \\
    RIMMA0360 & N/A & 18    & 1 \\
    RIMMA0362 & N/A & 8     & 1 \\
    RIMMA0363 & N/A & 16    & 1 \\
    RIMMA0370 & N/A & 17    & 1 \\
    RIMMA0372 & N/A & 24    & 1 \\
    RIMMA0373 & N/A & 22    & 1 \\
    RIMMA0408 & 478967 & 2     & 1 \\
    RIMMA0411 & 479044 & 1     & 1 \\
    RIMMA0413 & 484413 & 1     & 1 \\
    RIMMA0414 & 484421 & 1     & 1 \\
    RIMMA0424 & 485120 & 8     & 0.9 \\
    RIMMA0432 & 489126 & 1     & 1 \\
    RIMMA0434 & 490921 & 2     & 0.5 \\
    RIMMA0435 & 490973 & 1     & 1 \\
    RIMMA0442 & 537097 & 2     & 1 \\
    RIMMA0443 & 537099 & 2     & 1 \\
    RIMMA0444 & 538009 & 2     & 1 \\
    RIMMA0445 & 538011 & 2     & 1 \\
    RIMMA0446 & 539920 & 2     & 1 \\
    RIMMA0447 & 539921 & 2     & 1 \\
    RIMMA0448 & 539922 & 2     & 1 \\
    RIMMA0449 & 539923 & 2     & 1 \\
    RIMMA0450 & 539924 & 2     & 1 \\
    RIMMA0451 & 539926 & 2     & 1 \\
    RIMMA0452 & 539927 & 2     & 1 \\
    RIMMA0453 & 543843 & 2     & 1 \\
    RIMMA0454 & 543846 & 2     & 1 \\
    RIMMA0455 & 543847 & 2     & 1 \\
    RIMMA0456 & 543849 & 2     & 1 \\
    RIMMA0457 & 543850 & 2     & 1 \\
    RIMMA0458 & 547086 & 2     & 1 \\
    RIMMA0459 & 547088 & 2     & 1 \\
    RIMMA0483 & 600954 & 2     & 1 \\
    RIMMA0490 & 601003 & 2     & 1 \\
    RIMMA0515 & 601270 & 2     & 1 \\
    RIMMA0537 & 601416 & 2     & 1 \\
    RIMMA0550 & 601468 & 2     & 1 \\
    RIMMA0553 & 601489 & 2     & 1 \\
    RIMMA0559 & 601495 & 2     & 1 \\
    RIMMA0561 & 601497 & 2     & 1 \\
    RIMMA0562 & 601498 & 2     & 1 \\
    RIMMA0571 & 601562 & 2     & 1 \\
    RIMMA0572 & 601563 & 2     & 1 \\
    RIMMA0577 & 601568 & 2     & 1 \\
    RIMMA0579 & 601570 & 2     & 1 \\
    RIMMA0590 & 601724 & 2     & 1 \\
    RIMMA0591 & 601725 & 2     & 1 \\
    RIMMA0592 & 601729 & 2     & 1 \\
    RIMMA0593 & 601773 & 2     & 1 \\
    RIMMA0594 & 601774 & 2     & 1 \\
    RIMMA0595 & 601775 & 2     & 1 \\
    RIMMA0596 & 601776 & 2     & 1 \\
    RIMMA0597 & 601777 & 2     & 1 \\
    RIMMA0598 & 601778 & 2     & 1 \\
    RIMMA0599 & 601779 & 2     & 1 \\
    RIMMA0600 & 601780 & 2     & 1 \\
    RIMMA0601 & 601781 & 2     & 1 \\
    RIMMA0602 & 601782 & 2     & 1 \\
    RIMMA0603 & 601783 & 2     & 1 \\
    RIMMA0604 & 601784 & 2     & 1 \\
    RIMMA0605 & 601785 & 2     & 1 \\
    RIMMA0606 & 601786 & 2     & 1 \\
    RIMMA0607 & 601787 & 2     & 1 \\
    RIMMA0608 & 601788 & 2     & 1 \\
    RIMMA0609 & 601789 & 2     & 1 \\
    RIMMA0610 & 601790 & 2     & 1 \\
    RIMMA0611 & 601791 & 2     & 1 \\
    RIMMA0612 & 601792 & 2     & 1 \\
    RIMMA0613 & 601808 & 2     & 1 \\
    RIMMA0622 & 645837 & 2     & 0.5 \\
    RIMMA0624 & 645930 & 1     & 1 \\
    RIMMA0629 & 646057 & 2     & 0.5 \\
    RIMMA0631 & 646072 & 2     & 0.5 \\
    RIMMA0659 & 286729 & 2     & 1 \\
    RIMMA0660 & 485451 & 2     & 1 \\
    RIMMA0678 & 285833 & 1     & 1 \\
    RIMMA0681 & 628446 & 2     & 1 \\
    RIMMA0683 & 483568 & 2     & 1 \\
    RIMMA0684 & 28482 & 2     & 1 \\
    RIMMA0685 & 287623 & 4     & 1 \\
    RIMMA0693 & 487959 & 2     & 1 \\
    RIMMA0694 & 28487 & 2     & 1 \\
    RIMMA0695 & 28567 & 1     & 1 \\
    RIMMA0699 & 28465 & 2     & 1 \\
    RIMMA0704 & 28623 & 2     & 1 \\
    RIMMA0706 & 28615 & 2     & 1 \\
    RIMMA0711 & 29075 & 1     & 1 \\
    RIMMA0713 & 489399 & 2     & 1 \\
    RIMMA0715 & 28454 & 2     & 1 \\
    RIMMA0717 & 483926 & 2     & 1 \\
    RIMMA0718 & 484805 & 2     & 1 \\
    RIMMA0723 & 28565 & 2     & 1 \\
    RIMMA0724 & 490826 & 2     & 1 \\
    RIMMA0725 & 490827 & 1     & 1 \\
    RIMMA0728 & 484969 & 1     & 1 \\
    RIMMA0732 & 28456 & 2     & 1 \\
    RIMMA0734 & 26028 & 2     & 1 \\
    RIMMA0738 & N/A & 2     & 1 \\
    RIMMA0739 & N/A & 2     & 1 \\
    RIMMA0744 & N/A & 2     & 1 \\
    RIMMA0747 & N/A & 1     & 1 \\
    RIMMA0748 & N/A & 2     & 1 \\
    RIMMA0749 & N/A & 2     & 1 \\
    RIMMA0750 & N/A & 2     & 0.5 \\
    RIMMA0751 & N/A & 1     & 1 \\
    RIMMA0752 & N/A & 1     & 1 \\
    RIMMA0753 & N/A & 2     & 1 \\
    RIMMA0755 & N/A & 2     & 1 \\

@@

% Appendix S5. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.png}
    \flushleft{Figure S2: Neighbor-joining tree of the sequenced region in the 5' UTR (right; Region 1) and the 66,169 bp upstream region (left; Region 2) of \emph{tb1} using 10,000 bootstraps. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion. EjuA refers to individuals from population Ejutla A, EjuB from Ejutla B, SLO from San Lorenzo, and MSA from La Mesa. Remaining individuals are lines of maize (\emph{Zea mays} ssp. \emph{mays}).}
